Modeling Human Interactions in Collaborative Interactive Evolutionary Computation

### 2017-02-03 2017-GECCO-Modeling-User-Interactions-in-IEC/paper-body.tex
Typo arreglado
otro typo arreglado

Some C-IEC systems promote user engagement by presenting interesting information to 
users, for instance the genetic lineage of each phenotype or the most popular or 
best rated solucion\cite{picbreeder,forms}.In a recent work by 
Wagy \& Bongard \cite{wagy2014collective} user interaction 
is needed for evaluating the fitness and developing
new designs of robot locomotion. Collaboration is encouraged by gamifying the system 
using the maximum distance indicator to inspire the user to try and ``beat'' previous designs. 
In any case, using gamification techniques imply that we must deal with interactive evolutionary
system as socio-technical constructs, where the social aspects are
essential to understand its dynamics. In this sense, conclusions
reached with other systems such as NodEO \cite{DBLP:conf/gecco/MereloCGCRV16}
can also be applied to this system; and applying social 
network techniques such as graph analysis
to their study will allow us to understand them more thoroughly. 
% C-IEAS
Given the human fatigue limitation when applying IEAs, some authors 
have tried to mitigate the problem by allowing the algorithm to 
collaborate with the user, so that sometimes 
users perform the evaluation,  but also specific measures are included 
into the algorithm to perform the
evaluation of some features automatically. For instance, 
Reis et al. added some terrain measures (such as accessibility and edge length) 
to a standard  IEC in \cite{DBLP:journals/soco/FradeVC12}. 
This way the algorithm was capable of providing  terrains that would otherwise have need
users evaluation for these specific features. Seyama and Munetomo \cite{seyama2016development}
also propose the reduction of the user fatigue by using 
a collaborative filtering algorithm to show only the information utilized by similar users as 
they collaborate with a large number of users for the interactive modeling of 3D glasses. 
The framework and data model for 
representing the interactive process of C-IEC systems is proposed next
% Volunteer Based
% HBC
% Engagement Techniques
% Models

@@

\begin{itemize}
\item {\bf EvoSpace-Redis} 
EvoSpace is a population store \cite{Evospace}  for the development of 
evolutionary algorithms that are intended to run on a cloud computing model. 
The population is decoupled from any particular evolutionary algorithm. 
Candidate solutions are stored as of objects in a population, and they can be withdrawn, 
processed and replaced using a specified set of methods \cite{GValdez2015}. The population
is stored in-memory, using the Redis key-value database. Redis was chosen over a relational 
database management system, because it provides a hash based implementation of sets and 
queues which are natural data structures for the EvoSpace model. Basicaly a sample of 
candidate solutions are retieved from the server, evaluated, and then sent back. 
The same operations are used to Evolve the population. In EvoSpace individuals replaced 
in the population are stored indefinitly, to permit users to store permalinks to them.
Implementation details are presented in \cite{garcia2013evospace}.

>>>>

Some C-IEC systems promote user engagement by presenting interesting information to 
users, for instance the genetic lineage of each phenotype or the most popular or 
best rated solucion\cite{picbreeder,forms}.In a recent work by 
Wagy \& Bongard \cite{wagy2014collective} user interaction 
is needed for evaluating the fitness and developing
new designs of robot locomotion. Collaboration is encouraged by gamifying the system 
using the maximum distance indicator to inspire the user to try and ``beat'' previous designs. 
In any case, using gamification techniques imply that we must deal with interactive evolutionary
system as socio-technical constructs, where the social aspects are
essential to understand its dynamics. In this sense, conclusions
reached with other systems such as NodEO \cite{DBLP:conf/gecco/MereloCGCRV16}
can also be applied to this system; and applying social 
network techniques such as graph analysis
to their study will allow us to understand them more thoroughly. 
% C-IEAS
Given the human fatigue limitation when applying IEAs, some authors 
have tried to mitigate the problem by allowing the algorithm to 
collaborate with the user, so that sometimes 
users perform the evaluation,  but also specific measures are included 
into the algorithm to perform the
evaluation of some features automatically. For instance, 
Reis et al. added some terrain measures (such as accessibility and edge length) 
to a standard  IEC in \cite{DBLP:journals/soco/FradeVC12}. 
This way the algorithm was capable of providing  terrains that would otherwise have needed
users evaluation for these specific features. Seyama and Munetomo \cite{seyama2016development}
also propose the reduction of the user fatigue by using 
a collaborative filtering algorithm to show only the information utilized by similar users as 
they collaborate with a large number of users for the interactive modeling of 3D glasses. 
The framework and data model for 
representing the interactive process of C-IEC systems is proposed next
% Volunteer Based
% HBC
% Engagement Techniques
% Models

@@

\begin{itemize}
\item {\bf EvoSpace-Redis} 
EvoSpace is a population store \cite{Evospace}  for the development of 
evolutionary algorithms that are intended to run on a cloud computing model. 
The population is decoupled from any particular evolutionary algorithm. 
Candidate solutions are stored as of objects in a population, and they can be withdrawn, 
processed and replaced using a specified set of methods \cite{GValdez2015}. The population
is stored in-memory, using the Redis key-value database. Redis was chosen over a relational 
database management system, because it provides a hash based implementation of sets and 
queues which are natural data structures for the EvoSpace model. Basicaly a sample of 
candidate solutions are retrieved from the server, evaluated, and then sent back. 
The same operations are used to Evolve the population. In EvoSpace individuals replaced 
in the population are stored indefinitly, to permit users to store permalinks to them.
Implementation details are presented in \cite{garcia2013evospace}.
